---
title: "p8105 HW6"
author: "Yijin Serena Wang"
date: "`r Sys.Date()`"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(rnoaa)
library(readr)
library(ggplot2)
library(modelr)
library(broom)
library(ggridges)
```

## Problem 1

Download and clean data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
Create a function to extract r squared from linear model output
```{r}
get_r_squared_hat <- function(model) {
  model %>% 
    glance() %>%
    pull(r.squared)
}
```

Create a function to extract beta0/intercept from linear model output
```{r}
get_beta_0 <- function(model) {
 model %>%
    tidy() %>%
    filter(term == "(Intercept)") %>%
    pull(estimate)
    
}
```

Create a function to extract beta1/coef for tmin from linear model output
```{r}
get_beta_1 <- function(model) {
 model %>%
    tidy() %>%
    filter(term != "(Intercept)") %>%
    pull(estimate)
  }
```

Create 5000 bootstrap samples. For each sample, build a linear model then extract results.
```{r}
set.seed(1)
weather_sim_lm_result <- weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    r_squared_hat = map(models, get_r_squared_hat),
    beta_0 = map(models, get_beta_0),
    beta_1 = map(models, get_beta_1)) %>%
  select(r_squared_hat, beta_0, beta_1) %>%
  mutate(across(everything(), as.numeric)) %>%
  mutate(log_beta0_beta1 = log(beta_0 * beta_1))
```

Plot model results
```{r}
weather_sim_lm_result %>%
  pivot_longer(cols=c("r_squared_hat",
                      "log_beta0_beta1"), 
                      names_to = "statistics") %>%
  ggplot() +
  stat_density_ridges(
    aes(x = value, y = statistics),
    quantile_lines = TRUE, 
    quantiles = c(0.025, 0.975), 
    alpha = 0.7) +
  facet_grid(~statistics, scales = "free_x")
  

```

Based on the density plot, both statistics seem to follow a normal distribution.

